Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-23 manuscript/main.tex
expanded conclusion

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
 & Coefficient & p-value & Coefficient & p-value \\ 
\end{tabular}
\caption{Predicting aggregate cross-state alignment scores with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

@@

The log alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time. Where and when do similar policies cross state borders? Which legislators introduce similar legislation? Does lobbying by pressure groups result in the adoption of similar policies across states? Do similar patterns of campaign contributions to legislators predict similar policies in proposed legislation? Questions such as these can be directly investigated using the policy similarity measures we introduce.

A consistent result in our analysis is that the measure of policy similarity based on text reuse is high precision and low recall.  As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments, especially when considering measurements at the bill-level. This can be done through the use of quantile regression, or through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.

>>>>

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Wed Sep 21 20:12:14 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
   & Coefficient & p-value & Coefficient & p-value \\  \hline
Intercept & -33577305.967 & 0.997 & 10.041 & 0.000 \\ 
  Diffusion Tie & 2423709.311 & 0.042 & 0.266 & 0.050 \\ 
    Coverage & 10938819.897 & 0.000 & 1.379 & 0.000 \\ 
\hline
\end{tabular}
\caption{Predicting aggregate cross-state alignment scores with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

@@

The alignment scores we derive provide a resource for scholars to test hypotheses of the causes and consequences of the introduction and adoption of similar policies---a measure which crosses different policy areas, states, and time. In a validation experiment, we show that a wide span of quantiles of alignment scores between bills---from the median up through and above the 99$^{th}$ percentile---are negatively correlated with the ideological distance between the legislators who introduced the two bills. This result opens the door to many other hypotheses that could be tested using alignment scores for bill pairs.  Where and when do similar policies cross state borders? Which legislators introduce similar legislation? Does lobbying by pressure groups result in the adoption of similar policies across states? Do similar patterns of campaign contributions to legislators predict similar policies in proposed legislation? Questions such as these can be directly investigated using the policy similarity measures we introduce.

The nature of our measure of policy similarity based on text reuse is that it is high precision and low recall.  As such, in future research we advise scholars to focus on upper quantiles of the distribution of alignments when the inquiry requires the identification of bills that introduce equivalent policies. For predictive modeling, this can be done through the use of quantile regression at high quantiles. For searching out bill pairs, this can be done through thresholding on high alignment scores (e.g., 50+) to indicate the presence of highly similar policy proposals in legislation.
